### 2022-10-14 manuscript.Rmd
Change order of output file types
Clean up code style

output:
  papaja::apa6_docx: default
  papaja::apa6_pdf:
    latex_engine: xelatex

@@

      # Informed condition: Matching keywords and positive response
      "Informed" = item_id[
        phase == "Insight" & keywords == "Match" & response %in% c(3, 4)
      ],

      # Naive condition: Non-matching keywords and negative response
      "Naive" = item_id[
        phase == "Insight" & keywords == "Non-match" & response %in% c(1, 2)
      ],

      # Exclude: Matching keywords and negative response
      "Exclude_informed" = item_id[
        phase == "Insight" & keywords == "Match" & response %in% c(1, 2)
      ],

      # Exclude: Non-matching keywords and positive response
      "Exclude_naive" = item_id[
        phase == "Insight" & keywords == "Non-match" & response %in% c(3, 4)
      ],

      # Exclude: Positive response *before* any info was presented
      "Exclude_known" = item_id[phase == "Pre-insight" & response == 4]
    )
  })

@@

  # Process EEG data
  res <- pipeline$group_pipeline(
    vhdr_files = vhdr_files,
    log_files = logs,
    output_dir = output_dir,
    epochs_dir = here(output_dir, "epochs"),
    report_dir = report_dir,
    downsample_sfreq = 125.0,
    bad_channels = NULL,
    ica_method = "fastica",
    ica_n_components = 0.99,
    highpass_freq = 0.1,
    lowpass_freq = 30.0,
    triggers = c(221, 222),
    epochs_tmin = -0.5,
    epochs_tmax = 1.5,
    baseline = c(-0.2, 0.0),
    reject_peak_to_peak = 150.0,
    components = list(
      "name" = list("P1", "N170", "N400"),
      "tmin" = list(0.1, 0.15, 0.4),
      "tmax" = list(0.15, 0.2, 0.7),
      "roi" = list(
        c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
        c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
        c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
      )
    ),
    average_by = c("phase/condition"),
    perform_tfr = TRUE,
    tfr_subtract_evoked = FALSE,
    tfr_freqs = seq(4, 40, by = 1.0),
    tfr_cycles = seq(2, 20, by = 0.5),
    tfr_mode = "percent",
    tfr_baseline = c(-0.45, -0.05),
    perm_contrasts = list(
      c("Pre-insight/Informed", "Pre-insight/Naive"),
      c("Insight/Informed", "Insight/Naive"),
      c("Post-insight/Informed", "Post-insight/Naive"),
      c("Insight/Informed", "Insight/Exclude_informed")
    ),
    tfr_components = list(
      name = list("alpha_beta"),
      tmin = list(0.6),
      tmax = list(1.2),
      fmin = list(8.0),
      fmax = list(20.0),
      roi = list(c("P3", "Pz", "P4", "PO3", "POz", "PO4"))
    ),
    perm_tmin = -0.4,
    perm_tmax = 1.4,
    n_jobs = 1
  )
}

@@

  # Find the best fitting model (see Matuschek et al., 2017, *JML*)
  build <- buildmer(
    buildmerControl = buildmerControl(
      formula, data,
      args = list("control" = lme4::lmerControl(
        optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)
      )),
      direction = c("backward", "backward"),
      cl = cl,
      elim = LRTalpha(.20),
      calc.anova = TRUE,
      ddf = "Satterthwaite",
      dep = dep
    )
  )
  stopCluster(cl)

  # Compute marginal means and contrasts
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  specs <- pairwise ~ condition | phase
  means <- emmeans(build@model, specs = c("phase", "condition"))
  contrasts <- contrast(means, "pairwise", simple = "condition") %>%
    summary(by = NULL, adjust = "bonferroni")

  # Create list of returns
  list(
    "model" = build@model,
    "summary" = build@summary,
    "anova" = build@anova,
    "means" = means,
    "contrasts" = contrasts
  )
}

@@

  # Contrast coding for phase
  cbind(
    c("Pre-insight" = -1, "Insight" = 1, "Post-insight" = 0),
    c("Pre-insight" = 0, "Insight" = -1, "Post-insight" = 1)
  ) %>%
    t() %>%
    ginv() -> contrasts(trials_main$phase)

  # Contrast coding for condition
  cbind(c("Informed" = 1, "Naive" = -1)) %>%
    t() %>%
    ginv() -> contrasts(trials_main$condition)

@@

  # Contrast coding for phase
  cbind(
    c("Pre-insight" = -1, "Insight" = 1, "Post-insight" = 0),
    c("Pre-insight" = 0, "Insight" = -1, "Post-insight" = 1)
  ) %>%
    t() %>%
    ginv() -> contrasts(trials_control$phase)

  # Contrast coding for condition
  cbind(c("Informed" = 1, "Exclude_informed" = -1)) %>%
    t() %>%
    ginv() -> contrasts(trials_control$condition)

>>>>

output:
  papaja::apa6_pdf:
    latex_engine: xelatex
  papaja::apa6_docx: default

@@

      # Informed condition: Matching keywords and positive response
      Informed = item_id[
        phase == "Insight" & keywords == "Match" & response %in% c(3, 4)
      ],

      # Naive condition: Non-matching keywords and negative response
      Naive = item_id[
        phase == "Insight" & keywords == "Non-match" & response %in% c(1, 2)
      ],

      # Exclude: Matching keywords and negative response
      Exclude_informed = item_id[
        phase == "Insight" & keywords == "Match" & response %in% c(1, 2)
      ],

      # Exclude: Non-matching keywords and positive response
      Exclude_naive = item_id[
        phase == "Insight" & keywords == "Non-match" & response %in% c(3, 4)
      ],

      # Exclude: Positive response *before* any info was presented
      Exclude_known = item_id[phase == "Pre-insight" & response == 4]
    )
  })

@@

  # Process EEG data
  res <- pipeline$group_pipeline(
    vhdr_files = vhdr_files,
    log_files = logs,
    output_dir = output_dir,
    report_dir = report_dir,
    downsample_sfreq = 125.0,
    bad_channels = NULL,
    ica_method = "fastica",
    ica_n_components = 0.99,
    highpass_freq = 0.1,
    lowpass_freq = 30.0,
    triggers = c(221, 222),
    epochs_tmin = -0.5,
    epochs_tmax = 1.5,
    baseline = c(-0.2, 0.0),
    reject_peak_to_peak = 150.0,
    components = list(
      name = list("P1", "N170", "N400"),
      tmin = list(0.1, 0.15, 0.4),
      tmax = list(0.15, 0.2, 0.7),
      roi = list(
        c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
        c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
        c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
      )
    ),
    average_by = c("phase/condition"),
    perform_tfr = TRUE,
    tfr_subtract_evoked = FALSE,
    tfr_freqs = seq(4, 40, by = 1.0),
    tfr_cycles = seq(2, 20, by = 0.5),
    tfr_mode = "percent",
    tfr_baseline = c(-0.45, -0.05),
    perm_contrasts = list(
      c("Pre-insight/Informed", "Pre-insight/Naive"),
      c("Insight/Informed", "Insight/Naive"),
      c("Post-insight/Informed", "Post-insight/Naive"),
      c("Insight/Informed", "Insight/Exclude_informed")
    ),
    tfr_components = list(
      name = list("alpha_beta"),
      tmin = list(0.6),
      tmax = list(1.2),
      fmin = list(8.0),
      fmax = list(20.0),
      roi = list(c("P3", "Pz", "P4", "PO3", "POz", "PO4"))
    ),
    perm_tmin = -0.4,
    perm_tmax = 1.4
  )
}

@@

  # Find the best fitting model (see Matuschek et al., 2017, *JML*)
  build <- buildmer(
    buildmerControl = buildmerControl(
      formula, data,
      args = list(control = lme4::lmerControl(
        optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)
      )),
      direction = c("backward", "backward"),
      cl = cl,
      elim = LRTalpha(.20),
      calc.anova = TRUE,
      ddf = "Satterthwaite",
      dep = dep
    )
  )
  stopCluster(cl)

  # Compute marginal means and contrasts
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  means <- emmeans(build@model, specs = c("phase", "condition"))
  contrasts <- contrast(means, "pairwise", simple = "condition") %>%
    summary(by = NULL, adjust = "bonferroni")

  # Create list of returns
  list(
    model = build@model,
    summary = build@summary,
    anova = build@anova,
    means = means,
    contrasts = contrasts
  )
}

@@

  # Contrast coding for phase
  cbind(
    c(`Pre-insight` = -1, `Insight` = 1, `Post-insight` = 0),
    c(`Pre-insight` = 0, `Insight` = -1, `Post-insight` = 1)
  ) %>%
    t() %>%
    ginv() -> contrasts(trials_main$phase)

  # Contrast coding for condition
  cbind(c(`Informed` = 1, `Naive` = -1)) %>%
    t() %>%
    ginv() -> contrasts(trials_main$condition)

@@

  # Contrast coding for phase
  cbind(
    c(`Pre-insight` = -1, `Insight` = 1, `Post-insight` = 0),
    c(`Pre-insight` = 0, `Insight` = -1, `Post-insight` = 1)
  ) %>%
    t() %>%
    ginv() -> contrasts(trials_control$phase)

  # Contrast coding for condition
  cbind(c(`Informed` = 1, `Exclude_informed` = -1)) %>%
    t() %>%
    ginv() -> contrasts(trials_control$condition)
